Catchy Title

### 2011-10-11 proposal/paper.tex
Adding bulk of text

\section{Proposed Method}
\label{sec:proposed}
Our proposed method is as follows: ...

\section{Experiments}
\label{sec:experiments}
We implemented our method
and compared it with the older ones.
The results are very promising.

Figure \ref{fig:results} shows the results
(and, actually, how to insert postscript files):
\begin{figure}[htbf]
\begin{center}
\begin{tabular}{cc}
     % uncomment the next lines, and give the right ps files
     \psfig{figure=figs/data.ps,width=2in} &
     \psfig{figure=figs/plot.ps,width=2in} \\
    (a) & (b) 
\end{tabular}
\caption{A fictitious dataset (a) and its performance plot (b)}
\label{fig:results}
\end{center}
\end{figure}

\section{Conclusions}
\label{sec:conclusions}
The proposed method outperforms older approaches
in speed and quality.

\bibliography{christosref,other}
\bibliographystyle{plain}
\newpage
\pagenumbering{roman}
\tableofcontents

>>>>

\section{Proposed Method}
\label{sec:method}

\subsection{Data Collection}
\label{sec:method:data}
The data sets is mainly collected from two data centers: OpenCloud and DCO (?). OpenCloud is a CMU-based academic cluster consisting of 64 compute nodes, each with dual quad-core 2.83GHz Intel Xeon processors, 16GB memory and a 10GigE NIC, and Arista 10 GigE switches. OpenCluster mainly runs distributed services like Hadoop file systems and map reduce systems. We are collecting OS-level metrics and Hadoop system logs per 5 seconds, and have data over several months.

\subsection{Models}
\label{sec:method:models}
We will begin by using two existing correlation-based models on our dataset. One is SPIRIT, an incremental PCA approach that adapts the number of hidden variables \cite{Papdimitriou2005}. The datasets we consider are significantly less periodic and more bursty than the ones explored in the SPIRIT paper, and we may need to adjust the approach accordingly.

Another approach that we consider to learn a model for time series collected in a computer cluster is Kalman Filtering. Kalman Filter models are popularly used for time series modeling. \emph{Dynamic Data}, where temporal ordering of the data samples is important. The dynamic generative model given below, captures the state evolution dynamics of the data.

\begin{eqnarray}
x_{t+1} &=& Ax_t + w \\
y_t  &=& Cx_t + v
\end{eqnarray}

where A is the state transition matrix, C captures the observation model, w ~ N(0,Q) and v ~ N(0,R) are the state evolution and observation noise models respectively. The two main sub-problems associated with learning these models are \emph{inference} and \emph{parameter learning}. Inference deals with issues of estimating the unknown hidden variables given some observations and a given fixed model parameters. Parameter learning pertains to estimating the model parameters given only the  observations. The Expectation-Maximization (EM) algorithm is commonly used for parameter learning, while inference is done via maximum likelihood estimation.

Again as mentioned above, we will treat the multi-aspect data of the computing cluster in two different ways,

\begin{itemize}
\item Run kalman filtering on the different data streams from each machine individually.
\item Aggregate the data streams from all the machines to get a cluster level model for the data streams.
\end{itemize}

In addition to learning a model and using it to predict future patterns, we plan to do an analysis on existing data to observe important trends, such as bursts and repetitive patterns. Our main challenge in this problem is to deal with large data sets efficiently and flexibly. Our proposed direction is to build on the burst detection technique by Zhu et al. \cite{Zhu2003} and learn trends at different time scales and possibly with varied granularity of data aggregation across data center nodes.
Preprocessing

\subsection{Feature Extraction}
\label{sec:method:features}
We will perform two types of preprocessing on the raw data to produce candidate input that suits the filters we are testing. One is the log transform, in order to smooth high spikes expected in the data. The other is wavelet conversion, which would also be used for burst detection under different time windows.

\subsection{Scalability}
\label{sec:method:scale}
2) Large scale / parallel - once we pick one that seems to work well (Ilari)
   Can we get it running on Hadoop?
   Parallelizing implementation

\subsection{Anomaly Detection}
\label{sec:method:anomaly}
After validating the right model for our timeseries data from the data center, we plan to apply the model and combine it with anomaly detection algorithm. The first stage is to manually inject failures to tune the model to find out the anomalies. Later on, we can apply the algorithms on historical data from OpenCloud data center to test whether the algorithm can find anomalies in the system.

\bibliography{christosref,other}
\bibliographystyle{plain}
\newpage
\pagenumbering{roman}
